Machine Learning for Predictive Auto-Tuning with Boosted Regression Trees

### 2012-03-02 paper/final.tex
Aspell check

One strategy for addressing these challenges is to use one of a variety of
automatic methods known collectively as ``auto-tuning.'' Two major auto-tuning
approaches have emer-ged in the extensive literature covering the subject (see
surveys in e.g.
\citep{vuduc2001statistical, demmel2005self, vuduc2005oski, williams2008auto,
datta2008stencil, cavazos2008intelligent, li2009note, park2011evaluation}):
analytical model-driven optimization and empirical optimization
\citep{yotov2003comparison}.

@@

To addess this weakness, it is intuitively appealing to combine the two
approaches by first constraining the search space with an analytical model and
then exploring the reduced space empirically \citep{chen2005combining,
li2009note}. Unfortunately, such a hybrid approach is still bound by the quality
of the analytical model, which remains hard to build by hand.

@@

For the implementation features $b$, we directly used the integer and binary
values (block\_w, block\_h, etc.) that paramet-rized the kernels.  We did not
use platform features ($c$) in our experiments. We leave the investigation of
cross-platform predictive auto-tuning for future work.

>>>>

One strategy for addressing these challenges is to use one of a variety of
automatic methods known collectively as ``auto-tuning.'' Two major auto-tuning
approaches have emerged in the extensive literature covering the subject (see
surveys in e.g.
\citep{vuduc2001statistical, demmel2005self, vuduc2005oski, williams2008auto,
datta2008stencil, cavazos2008intelligent, li2009note, park2011evaluation}):
analytical model-driven optimization and empirical optimization
\citep{yotov2003comparison}.

@@

To address this weakness, it is intuitively appealing to combine the two
approaches by first constraining the search space with an analytical model and
then exploring the reduced space empirically \citep{chen2005combining,
li2009note}. Unfortunately, such a hybrid approach is still bound by the quality
of the analytical model, which remains hard to build by hand.

@@

For the implementation features $b$, we directly used the integer and binary
values (block\_w, block\_h, etc.) that paraded-raced the kernels.  We did not
use platform features ($c$) in our experiments. We leave the investigation of
cross-platform predictive auto-tuning for future work.
